Scheduling and Amortization for MPC

### 2021-11-21 paper_SIMD.tex
Fixed typo.

The dependence graph computes def-use edges:

\begin{itemize}
\item same-level $X\rightarrow Y$ where $X = ...$ and $Y = ...$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. 
\item outer-to-inner $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$.
\item inner-to-outer $X\rightarrow Y$ where $X$ is in an inner loop nest, $i_1,i_2,...i_j,...,i_k$, and $Y$ is in an outer one, $i_1,i_2,...i_j$. E.g. $\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$ to
$\texttt{c} = \mathit{CMP}(\texttt{sum}_1,\texttt{min}_0)$ is an inner-to-outer edge.
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge.
\item outer-to-inner back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in an immediately nested loop of $Y$'s loop. 
 \end{itemize}

We also define the $\mathit{closure}(n)$ where $n$ is a phi-node. Intuitively, it computes the set of statements that form a cycle in the loop with $n$. The closure of $n$ is defined as follows:
\begin{itemize}
\item $n$ is in $\mathit{closure}(n)$
\item $X$ is in $\mathit{closure}(n)$ if there is a same-level path from $n$ to $X$, and $X \rightarrow n$ is a same-level back-edge. 
\item $Y$ is in $\mathit{closure}(n)$ if there is a same-level path from $n$ to $Y$ and there is a same-level path from $Y$ to some $X$ in $\mathit{closure}(n)$.
\end{itemize}

@@

\ana{Add back-edges into Phase 1. A back-edge from a non-phi-node in loop $i$ to a phi-node in loop $i$'s header is a same-level edge. The only difference with the handling of normal def-use is that the operand index will become $i-1$. A back edge from a phi-node in loop $j$ to a phi-node in loop $i$, where $j$ is immediately nested in $i$ is an inner-to-outer edge and will require dropping dimension. We can show these are the only kinds of back-edges that may occur.}

@@

\FOR {each dimension $d$ from highest to 0}
\FOR {each $\phi$-node $n$ in loop $i_1,...,i_k$}
\STATE {compute $\mathit{closure}(n)$}
\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE 
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_k = 0; ...$ loop}  
\STATE {add $\phi$-nodes in $cl$ to header block} 
\STATE {add statements in $cl$ to loop body in some order of dependences} 
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_k}$ to $i_k$ in all statements in loop}
\STATE {treat FOR loop as monolith node: change def-use edges accordingly.}
\ENDFOR
\ENDFOR
\ENDFOR

@@

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$}
\STATE {$\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$}
\STATE {$\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$}
\STATE {$\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{c} = \mathit{CMP}(\texttt{sum}_1,\texttt{min}_0)$}
\STATE {$\texttt{index}_1 = \mathit{MUX}(\texttt{c},\texttt{index}_1,i)$}
\STATE {$\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$}
\STATE \COMMENT {End of outer loop $i$.}

@@

The transformation preserves the dependence edges. It raises the dimensions of scalars and optimistically vectorizes all operations. The last phase discovers loop-carried dependences and removes affected vectorization.

@@

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUM}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_1[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_1[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Starting at the inner phi-node $\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j], [0,0,...])$, the algorithm first computes it's closure. The closure amounts to the phi-node itself and $\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The algorithm adds same-level edges, one from $\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = ...$ to the monolithic FOR-loop node, and one from the FOR-loop node to $\texttt{c}[\stackrel{\rightarrow}{i}] = ...$.

@@

\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_1[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_1[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Next, analysis moves to outer dimension $i$. There are two phi-nodes, $\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$ and $\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$.
The closure of the first is 
\[
\begin{array}{l}
\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1), \\ 
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_1[\stackrel{\rightarrow}{i}],[0,1,...N]) 
\end{array}
\]
and the closure of the second one is
\[
\begin{array}{l}
\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000) \\
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_1[\stackrel{\rightarrow}{i}])
\end{array}
\]
Since the two closures intersect, we merge them into a single loop. We can now rewrite those statements, getting rid of the vectorization on $i$ in second FOR loop. Notably, the SUB and MUL computations are fully vectorizable and the ADD computation is vectorizable across the $i$-dimension.

@@

\STATE 
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUM\_SIMD}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL\_SIMD}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$} \\
\STATE {} 
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {FOR j=0; j<=D; j++} \COMMENT{ Turns into a MOTION loop, was $j$-loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD\_SIMD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE {} 
\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {} 
\STATE {$\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$} 
\STATE {$\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$}
\STATE {FOR i=0; i<=N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{c}[{i}] = \mathit{CMP}(\texttt{sum}'_1[{i}],\texttt{min}_0[{i}])$}
\STATE \hspace{0.25cm}{$\texttt{index}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{index}_1[{i}],[0,1,...N])$}
\STATE \hspace{0.25cm}{$\texttt{min}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{sum}'_1[{i}],\texttt{min}_1[{i}])$}

>>>>

The dependence graph has the following def-use edges:

\begin{itemize}
\item same-level (forward) $X\rightarrow Y$ where $X = ...$ and $Y = ...$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. 
\item outer-to-inner (forward) $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$.
\item inner-to-outer (forward) $X\rightarrow Y$ where $X$ is in an inner loop nest, $i_1,i_2,...i_j,...,i_k$, and $Y$ is in an outer one, $i_1,i_2,...i_j$. E.g. $\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$ to $\texttt{c} = \mathit{CMP}(\texttt{sum}_1,\texttt{min}_0)$ is an inner-to-outer edge.
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge.
\item outer-to-inner back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in an immediately nested loop of $Y$'s loop. 
 \end{itemize}

We also define $\mathit{closure}(n)$ where $n$ is a phi-node. Intuitively, it computes the set of nodes (i.e., statements) that form a dependence cycle with $n$. \ana{Cycle(n) is probably a better name.} The closure of $n$ is defined as follows:
\begin{itemize}
\item $n$ is in $\mathit{closure}(n)$
\item $X$ is in $\mathit{closure}(n)$ if there is a same-level path from $n$ to $X$, and $X \rightarrow n$ is a same-level back-edge. 
\item $Y$ is in $\mathit{closure}(n)$ if there is a same-level path from $n$ to $Y$ and there is a same-level path from $Y$ to some $X$ in $\mathit{closure}(n)$.
\end{itemize}

@@

\ana{Add back-edges into Phase 1. A back-edge from a non-phi-node in loop $i$ to a phi-node in loop $i$'s header is a same-level edge. The only difference with the handling of normal same-level forward def-use is that the operand index will become $i-1$. A back edge from a phi-node in loop $j$ to a phi-node in loop $i$, where $j$ is immediately nested in $i$ is an inner-to-outer edge and will require dropping dimension. We can show these are the only kinds of back-edges that may occur.}

@@

\FOR {each dimension $d$ from highest to 0}
\FOR {each $\phi$-node $n$ in loop $i_1,...,i_k$}
\STATE {compute $\mathit{closure}(n)$}
\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE 
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_k = 0; ...$ loop}  
\STATE {add $\phi$-nodes in $cl$ to header block} 
\STATE {add statements in $cl$ to loop body in some order of dependences} 
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_k}$ to $i_k$ in all statements in loop}
\STATE {treat FOR loop as monolith node: change def-use edges accordingly. Some edges become same-level.}
\ENDFOR
\ENDFOR
\ENDFOR

@@

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$}
\STATE {$\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$}
\STATE {$\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$}
\STATE {$\texttt{sum}_1 = \texttt{ADD}(\texttt{sum}_0,\texttt{p})$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{c} = \mathit{CMP}(\texttt{sum}_1,\texttt{min}_0)$}
\STATE {$\texttt{index}_1 = \mathit{MUX}(\texttt{c},\texttt{index}_0,i)$}
\STATE {$\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{min}_0,\texttt{sum}_1)$}
\STATE \COMMENT {End of outer loop $i$.}

@@

The transformation preserves the dependence edges. It raises the dimensions of scalars and optimistically vectorizes all operations. The next phase discovers loop-carried dependences and removes affected vectorization.

@@

\STATE \COMMENT {Begin of inner loop $j$.}
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUM}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE \COMMENT {End of inner loop $j$.}
\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Starting at the inner phi-node $\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j], [0,0,...])$, the algorithm first computes its closure. The closure amounts to the phi-node itself and $\texttt{sum}_1[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{ADD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The algorithm adds same-level edges, one from $\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = ...$ to the monolithic FOR-loop node, and one from the FOR-loop node to $\texttt{c}[\stackrel{\rightarrow}{i}] = ...$.

@@

\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {$\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}])$}
\STATE {$\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N])$}
\STATE {$\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}])$}
\STATE \COMMENT {End of outer loop $i$.}

@@

Next, analysis moves to outer dimension $i$. There are two phi-nodes, $\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$ and $\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$.
The closure of the first is 
\[
\begin{array}{l}
\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1), \\ 
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{index}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{index}_0[\stackrel{\rightarrow}{i}],[0,1,...N]) 
\end{array}
\]
and the closure of the second one is
\[
\begin{array}{l}
\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000) \\
\texttt{c}[\stackrel{\rightarrow}{i}] = \mathit{CMP}(\texttt{sum}'_1[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}]), \\
\texttt{min}_1[\stackrel{\rightarrow}{i}] = \mathit{MUX}(\texttt{c}[\stackrel{\rightarrow}{i}],\texttt{min}_0[\stackrel{\rightarrow}{i}],\texttt{sum}'_1[\stackrel{\rightarrow}{i}])
\end{array}
\]
Since the two closures intersect, we merge them into a single loop. We can now rewrite those statements, getting rid of the vectorization on $i$ in second FOR loop. Notably, the SUB and MUL computations are fully vectorizable and the ADD computation is vectorizable across the $i$-dimension.

@@

\STATE 
\STATE {$\texttt{C}'[i,j] = \mathit{raise\_dim}(\texttt{C}[j],i)$}
\STATE {$\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{SUM\_SIMD}(\texttt{S}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}], \texttt{C}'[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$}
\STATE {$\texttt{p}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}] = \mathit{MUL\_SIMD}(\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}],\texttt{d}[\stackrel{\rightarrow}{i},\stackrel{\rightarrow}{j}])$} \\
\STATE {} 
\STATE {$\texttt{sum}_0[i,j] = \phi(\texttt{sum}_1[i,j-1], [0,0,...])$}
\STATE {FOR j=0; j<=D; j++} \COMMENT{ Turns into a MOTION loop, was $j$-loop.}
\STATE \hspace{0.25cm}{$\texttt{sum}_1[\stackrel{\rightarrow}{i},{j}] = \mathit{ADD\_SIMD}(\texttt{sum}_0[\stackrel{\rightarrow}{i},{j}],\texttt{p}[\stackrel{\rightarrow}{i},{j}])$}
\STATE {} 
\STATE {$\texttt{sum}'_1[i] = \mathit{drop\_dim}(\texttt{sum}_1[i,j],j)$}
\STATE {} 
\STATE {$\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$} 
\STATE {$\texttt{min}_0[i] = \phi(\texttt{min}_1[i-1], 10000)$}
\STATE {FOR i=0; i<=N; i++} \COMMENT{ Turns into a MOTION loop, was $i$-loop.}
\STATE \hspace{0.25cm}{$\texttt{c}[{i}] = \mathit{CMP}(\texttt{sum}'_1[{i}],\texttt{min}_0[{i}])$}
\STATE \hspace{0.25cm}{$\texttt{index}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{index}_0[{i}],[0,1,...N])$}
\STATE \hspace{0.25cm}{$\texttt{min}_1[{i}] = \mathit{MUX}(\texttt{c}[{i}],\texttt{min}_0[{i}],\texttt{sum}'_1[{i}])$}
